Mitigation Strategies

### 2022-08-12 dev/notebooks/mitigation_strategies.qmd
uh

```{julia}
generators = Dict(
    :REVISE=>GenericGenerator(decision_threshold=0.5),
    :REVISE_conservative=>GenericGenerator(decision_threshold=0.9),
    :Gravitational=>GravitationalGenerator(),
    :ROAR=>ClapROARGenerator()
)
```

@@

```{julia}

```

>>>>

```{julia}
generators = Dict(
    :REVISE=>GenericGenerator(decision_threshold=0.5),
    :REVISE_conservative=>GenericGenerator(decision_threshold=0.9),
    :Gravitational=>GravitationalGenerator(),
    :ClapROAR=>ClapROARGenerator()
)
```

@@
